Untitled

### 2017-07-20 PaperCode.Rmd
Exploring B type  and "other"
Started looking into the strange behaviour of B property and Other property

ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)

@@

#Cornwall

@@

#Devon

@@

@@

#Somerset

@@

#Dorset

```{r}
BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))
```

#Suffolk

@@

#Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

@@

#Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()

@@

@@

@@

@@

@@

Combine1 <- BootResSummaryData(BootStrapRES)

Combine2 <- BootResSummaryData(BootStrapRESA)

Combine3 <- BootResSummaryData(BootStrapRESB)

@@

@@

Combine1 %>% ggplot(.,aes(x= maxPerc, y = abs(Percdiff))) + geom_point()

>>>>

#hide plot
#ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)

@@

#SouthWest

##Cornwall

@@

##Devon

@@

PlymouthDATA <- read_excel("PlymouthDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData(lowuse = 4:8)

@@

##Somerset

@@

##Dorset

```{r}
BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

ChristchurchDATA <- read_excel("Christchurch FOI17 - 0312 - Bourne - Ctax Discounts and Exemptions.xls",
                               sheet=1)[1:4] %>%
  StructureData(lowuse = c(6,12:17,20))

##Wiltshire

```{r}
#Wiltshire have not included everything
# WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts.xlsx",
#                                sheet=1)[1:4] %>%
#   StructureData()
```

#East of England

##Suffolk

@@

##Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

@@

##Cambridge
```{r}
EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
  StructureData()

@@

#North East

##Tyneside

setwd(file.path(RegionsComp, "Region North East"))
#Not sure all are there ask for confirmation
# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(2:4,6,8:10))

@@

#Strangely low numbers checking
# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(3,5:6))

@@

land registry 
sue gambles

@@

#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
CurrentLADS <- ls(pattern = "DATA") %>%
  map_chr(~{df<- get(.x)
  df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] }
)

@@

Combine1 <- BootResSummaryData(BootStrapRES) %>% mutate(LAD11CD = CurrentLADS)

Combine2 <- BootResSummaryData(BootStrapRESA) %>% mutate(LAD11CD = CurrentLADS)

Combine3 <- BootResSummaryData(BootStrapRESB) %>% mutate(LAD11CD = CurrentLADS)

@@

HouseMatch <- data_frame(PropType = "D,S,T,F,O" %>% str_split(",") %>% unlist,
type = "Detached,Semi-Detached,Terraced,Flats/Maisonettes,Other"%>% str_split(",") %>% unlist)

#test CoL after adding in filtering for other LADs
testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000)
testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A")
testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B")

testColA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

testColA %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

test <- CoLLONDATA %>% SubsetPrice() %>% left_join(HouseMatch)
testB <- CoLLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- CoLLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)

test <- CoLLONDATA %>% SubsetPrice("A")

CoLnums <- BootStrapRES$CoLLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

CoLnumsA <- BootStrapRESA$CoLLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean(., na.rm = TRUE)))

table(test$type, test$class)
table(testA$type, testA$class)
table(testB$type, testB$class)

LADNMs <- EW2 %>% group_by(LAD11CD) %>%
  summarise(LAD11NM = first(LAD11NM))

PropertyTypes <- c("D", "S", "T", "F")

ABratio <- prices %>% 
  filter(X5 %in% PropertyTypes) %>%
  group_by(Admin_district_code, X15) %>%
  summarise(count = n(), 
            mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code)

ABratio2 <- ABratio%>%
  select(-mean) %>%
spread(key = X15, value = count) %>%
  mutate(Countratio = B/(A+B))

ABratio3 <- ABratio%>%
  select(-count) %>%
spread(key = X15, value = mean) %>%
  mutate(Valueratio = B/(A))

ABratio4 <-  left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
  left_join(LADNMs) %>%
  left_join(prices %>% 
  group_by(Admin_district_code) %>%
summarise(mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code))

sum(prices$X15 == "B")/nrow(prices)

test <- ABratio4 %>% 
  filter(LAD11CD %in% CurrentLADS)

ABratio3 %>% ggplot(., aes(x = Valueratio)) +geom_density()

test <- Combine1 %>% 
  left_join(ABratio4)

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()

test %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()

@@
